### 2016-10-20 paper/evaluation.tex
comments to jean; adding initial title (to help keep the focus)

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from Github. We are
interested in opportunities to improve performance of test execution
with parallelism \Jbc{Should we use the term parallelism indistinctly
to refer to multi-process and multi-threaded execution?}, measure the
obtained gain (if any), and discuss the major concerns that affect
performance based on the obtained findings.  We pose the following
research questions:

>>>>

\Mar{I think the high-level goal should be something along the lines
  of understanding prevalence of long test runs and main sources of
  cost in open-source Java projects.  Intuitively, the problem should
  come before the solution :).  Based on that, we study
  parallelization of testing frameworks.  More precisely, we
  investigage how prevalent test parallelization is, the potential for
  improving execution cost, issues of flakiness that hinders use of
  parallelization, and how to address those issues.}

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from Github. We are
interested in opportunities to improve performance of test execution
with parallelism \Jbc{Should we use the term parallelism indistinctly
to refer to multi-process and multi-threaded execution?}\Mar{I think I
used the term low-level parallelism on intro to make this distiction.
Please confirm if that is correct and coherent with what you want to
say.  If yes, use this term.}, measure the
obtained gain (if any), and discuss the major concerns that affect
performance based on the obtained findings. We pose the followinga
research questions:
